Operation Mode Study in Cloud Manufacturing Ecosystem

### 2016-09-09 design.tex
tao's comment

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows for the original mode, while in other extension, some of the assumptions will be modified.
\begin{compactitem}
\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
\item The quality of product is determined by the worst quality of the selected resource;
\item Resource are renewable that the available capacity will be restored when the processing procedure finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and processing procedure cannot be interrupted;
\item Provider can only schedule task-parts in inactive status.
\end{compactitem}

>>>>

% \subsubsection{Assumptions} % (fold)
% \label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows for the original mode, while in other extension, some of the assumptions will be modified.
\begin{compactitem}
\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
\item The quality of product is determined by the worst quality of the selected resource;
\item Resource are renewable that the available capacity will be restored when the processing procedure finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and processing procedure cannot be interrupted;
\item Provider can only schedule task-parts in inactive status.
\end{compactitem}
